Price of Anarchy for Mean Field Games

### 2018-07-26 PoA.tex
sketch of Prop 7 Case 4

	(ToDo: Show $(\bar{b}_1-B u_0^{\bar{b}_1}) \to 0$.)

	Let $\zeta_2>0$. Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2 \int_0^{\frac{T}{2}}e^{2tb_1}e^{-2t\zeta_2}dt=:c_{\Delta SC}>0,
	\end{equation*}
	and therefore:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0.
	\end{equation*}
	Thus, we conclude:
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty,
	\end{split}
	\end{equation*}
	and therefore,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
	\end{equation*}

>>>>

	(ToDo: Show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) \geq 0$.)

	Next, we show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) \geq 0$. We have: (ToDo don't use $\xi$, add superscripts)
	\begin{equation*} 
	\bar{b}_1-Bu^{\bar{b}_1}_0=\frac{BD(\bar{b}_1-\delta^+_u)-\delta^-_u\bar{b}_1-BC+(BC+BD\delta^-_u+\delta^+_u\bar{b}_1-BD\bar{b}_1)e^{-(\delta^+_u-\delta^-_u)T}}{-\delta^-_u+BD+(\delta^+_u-BD) e^{-(\delta^+_u-\delta^-_u)T}}
	\end{equation*}

	Let $\zeta_2>0$. Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) \geq 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2 \int_0^{\frac{T}{2}}e^{2tb_1}e^{-2t\zeta_2}dt=:c_{\Delta SC}>0,
	\end{equation*}
	and therefore:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0.
	\end{equation*}
	Thus, we conclude:
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty,
	\end{split}
	\end{equation*}
	and therefore,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
	\end{equation*}
